Early Observations of \abc:\\ \textbf{a Type Ia Supernova Featuring Either} Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-11-15 doc/ms.tex
Add caption for the dessart figure

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{compare_Dessart.pdf}
  \caption{
  }
  \label{fig:dessart}
\end{figure}

\textbf{In Figure~\ref{fig:dessart} we compare photometric
observations of \abc\ to the large-$^{56}$Ni yield DD and PDD
models presented in \citet{2014MNRAS.441..532D}. DD and PDD models
with $M_\mathrm{Ni}/M_\odot \la 0.7$ and 0.5, respectively, fail to
match the early luminosity and blue colors of \abc. The PDD models
provide a better match to the observations than the DD models. The
PDD models evolve more rapidly towards blue colors and provide a
better match to the $g$-band flux in the days after explosion.
Furthermore, unlike the DD models, the PDD models exhibit strong
\ion{C}{2} lines that gradually disappear in the $\sim$week after
explosion \citet{2014MNRAS.441..532D}. In detail, the early wiggles
in the \abc\ light curve are not matched by the PDD models, which
exhibit more smooth variations. Nevertheless, the PDD models
presented in \citet{2014MNRAS.441..532D} provide several attractive
explanations for the unusual features in the early behavior of
\abc, and small adjustments to the model (e.g., additional mixing
of the radioactive material, which \citeauthor{2014MNRAS.441..532D}
only explore for the DD model) may better match \abc. }

>>>>

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{compare_Dessart.pdf}
  \caption{ \textbf{Comparison of the DD and PDD models of
  \citet{2014MNRAS.441..532D} to the \abc\ $g$-band light curve
  (top) and the $(B-V)_0$ color curve. We have translated each
  light curve to match the LCO observations $\sim$1.7\,d after
  $t_0$ given the uncertain time of explosion. Translational
  offsets are listed in the bottom panel legend, which shows the
  models in order of decreasing $M_\mathrm{Ni}$ from top to bottom.
  DD models (labeled as DDC to match the nomenclature of
  \citealt{2014MNRAS.441..532D}) are shown as dash-dot lines, while
  PDD models (labeled as PDDEL) are shown as dashed lines. The PDD
  models provide a better match to the observations.}
  }
  \label{fig:dessart}
\end{figure}

\textbf{In Figure~\ref{fig:dessart} we compare photometric
observations of \abc\ to the large-$^{56}$Ni yield DD and PDD
models presented in \citet{2014MNRAS.441..532D}. DD and PDD models
with $M_\mathrm{Ni}/M_\odot \la 0.7$ and 0.5, respectively, fail to
match the early luminosity and blue colors of \abc. The PDD models
provide a better match to the observations than the DD models. The
PDD models evolve more rapidly towards blue colors and provide a
better match to the $g$-band flux in the days after explosion.
Furthermore, unlike the DD models, the PDD models exhibit strong
\ion{C}{2} lines that gradually disappear in the $\sim$week after
explosion \citet{2014MNRAS.441..532D}. In detail, the early wiggles
in the \abc\ light curve are not matched by the PDD models, which
exhibit more smooth variations. Furthermore, while the focus of
this study is the early evolution of \abc, the PDD models evolve
more rapidly to the red post-peak than the observations.
Nevertheless, the PDD models presented in
\citet{2014MNRAS.441..532D} provide several attractive explanations
for the unusual features in the early behavior of \abc, and small
adjustments to the model (e.g., additional mixing of the
radioactive material, which \citeauthor{2014MNRAS.441..532D} only
explore for the DD model) may better match \abc. }
